### 2011-05-11 paper.tex
Fixed statement of polytime reductions

\begin{prop}
Let $C$ be a $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class and let $T$ be a mapping $\{0,1\}^n \to \{0,1\}^m$ defined by a polynomial time Turing machine. Then if $f \circ T \in C$, $f \in C$.
\end{prop}

@@

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
We wish to show that if $f\circ T \in \Sigma \cdot C$, then $f \in \Sigma \cdot C$. Let $g$ be the partial function in $C$ such that if $f(T(x)) = 1$, then there exists $y\in\{0,1\}^{p(|T(x)|)} = \{0,1\}^{p'(|x|)}$ such that $g(\langle T(x),y\rangle) = 1$ and if $f(T(x)) = 0$, then for all $y$ $g(\langle T(x),y\rangle) = 0$. There exists a polynomial time Turing machine $T'$ that takes $\langle x, y\rangle$ to $\langle T(x), y\rangle$, so the function $h(\langle x, y\rangle) = g(\langle T(x), y\rangle)$ is in $C$.

Note that if $f(x) = 1$, then $f(T(x)) = 1$, so there exists $y$ such that $h(\langle x, y\rangle) = g(\langle T(x),y\rangle) = 1$, and if $f(x) = 0$, then for all $y$, $h(\langle x, y\rangle) = g(\langle T(x),y\rangle) = 0$, so since $h \in C$, $f \in \Sigma \cdot C$.
\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Pi \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

>>>>

\begin{prop}
Let $C$ be a $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class and let $T$ be a mapping $\{0,1\}^n \to \{0,1\}^m$ defined by a polynomial time Turing machine. Then if $f \in C$, $f\circ T \in C$.
\end{prop}

@@

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
\end{proof}
We wish to show that if $f \in \Sigma \cdot C$, then $f \circ T \in \Sigma \cdot C$. We have that 
\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Pi \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
